---
title: "Adult Learn Comprehensive R Mathematics"
output: github_document
---

```r
<!-- ├── adult-learn.Rproj -->
<!-- ├── clique.community.Rd -->
<!-- ├── draw.plotmath.cell.Rd -->
<!-- ├── draw.title.cell.Rd -->
<!-- ├── factor.ecme.Rd -->
<!-- ├── factor.em.Rd -->
<!-- ├── factor.loglik.max.Rd -->
<!-- ├── factor.loglik.Rd -->
<!-- ├── F_carr_func.Rd -->
<!-- ├── file_ext.Rd -->
<!-- ├── F_non_func.Rd -->
<!-- ├── foo.Rd -->
<!-- ├── get.c.Rd -->
<!-- ├── get.r.Rd -->
<!-- ├── license -->
<!-- ├── make.table.Rd -->
<!-- ├── matrix -->
<!-- │   └── gnu -->
<!-- │       ├── bin -->
<!-- │       │   ├── adultLearn.R -->
<!-- │       │   ├── adultParent.R -->
<!-- │       │   ├── Rprof.out -->
<!-- │       │   └── valueFilter.R -->
<!-- │       ├── doc -->
<!-- │       │   ├── adultLearn.md -->
<!-- │       │   ├── adultLearn.Rmd -->
<!-- │       │   ├── developIntro.html -->
<!-- │       │   ├── developIntro.Rmd -->
<!-- │       │   ├── futureOverview.html -->
<!-- │       │   └── futureOverview.Rmd -->
<!-- │       ├── image -->
<!-- │       │   ├── arithmetic-operators-list-2.png -->
<!-- │       │   ├── arithmetic-operators-list-3.png -->
<!-- │       │   ├── arithmetic-operators-list-4.png -->
<!-- │       │   ├── arithmetic-operators-list-5.png -->
<!-- │       │   ├── arithmetic-operators-list-6.png -->
<!-- │       │   ├── arithmetic-operators-list.png -->
<!-- │       │   ├── arithmetic-operators.png -->
<!-- │       │   ├── church-networks.png -->
<!-- │       │   ├── delta-church-networks.png -->
<!-- │       │   ├── dim-row-column.png -->
<!-- │       │   ├── lifecyclesavings-data.png -->
<!-- │       │   ├── linear-carrier-group-non-group.png -->
<!-- │       │   ├── linear-estimated-cumulative-2.png -->
<!-- │       │   ├── linear-estimated-cumulative.png -->
<!-- │       │   ├── network-cells-matrix-linear.png -->
<!-- │       │   ├── networks-cells-matrix-linear-color.png -->
<!-- │       │   ├── networks-cells-multiples-show.png -->
<!-- │       │   ├── networks-cells-rbeejs-2.png -->
<!-- │       │   ├── networks-cells-rbeejs.png -->
<!-- │       │   └── networks-cells-show.png -->
<!-- │       ├── pdf -->
<!-- │       │   ├── adultLearn-concordance.tex -->
<!-- │       │   ├── adultLearn.log -->
<!-- │       │   ├── adultLearn.pdf -->
<!-- │       │   ├── adultLearn.Rnw -->
<!-- │       │   ├── adultLearn.synctex.gz -->
<!-- │       │   ├── adultLearn.tex -->
<!-- │       │   ├── adultParent-concordance.tex -->
<!-- │       │   ├── adultParent.log -->
<!-- │       │   ├── adultParent.pdf -->
<!-- │       │   ├── adultParent.Rnw -->
<!-- │       │   ├── adultParent.synctex.gz -->
<!-- │       │   ├── adultParent.tex -->
<!-- │       │   ├── design-issues-concordance.tex -->
<!-- │       │   ├── design-issues.log -->
<!-- │       │   ├── design-issues.pdf -->
<!-- │       │   ├── design-issues.Rnw -->
<!-- │       │   ├── design-issues.synctex.gz -->
<!-- │       │   ├── design-issues.tex -->
<!-- │       │   ├── Rplots.pdf -->
<!-- │       │   ├── Rprof.out -->
<!-- │       │   └── Sweavel.sty -->
<!-- │       └── profile -->
<!-- │           ├── adultLearn.Rprofvis -->
<!-- │           └── adultParent.Rprofvis -->
<!-- ├── myimage.Rd -->
<!-- ├── my_sum.Rd -->
<!-- ├── pause.Rd -->
<!-- ├── plot.default.Rd -->
<!-- ├── plot.default.Rd.Rd -->
<!-- ├── %<-%.Rd -->
<!-- ├── readme_files -->
<!-- │   └── figure-gfm -->
<!-- │       └── pressure-1.png -->
<!-- ├── readme.md -->
<!-- ├── readme.Rmd -->
<!-- ├── Rprof.out -->
<!-- ├── S2.Rd -->
<!-- └── Sweavel.sty -->
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
